---
title: "Title of Analysis Goes Here"
author: "Your Name (netid@illinois.edu)"
date: "Insert Date Here"
output:
  html_document: 
    theme: default
    toc: yes
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = 'center')
```

```{r, load-packages, include = FALSE}
# load packages
```

```{r make-data, warning = FALSE, message = FALSE}
# read data and subset
source("make-data.R")
```

```{r read-full-data, warning = FALSE, message = FALSE}
# read full data
cc = data.table::fread("data/cc.csv.gz")
```

```{r read-subset-data, warning = FALSE, message = FALSE}
# read subset of data
cc_sub = data.table::fread("data/cc-sub.csv")
```

***

## Abstract

> Abstract text goes here.

***

## Introduction

Write your introduction here.

***

## Methods

Describe the methods used in this section.

### Data

Specifically describe the data and how it is used here.

### Modeling

Discuss your modeling and validation strategy here.

***

## Results

State your results here.

***

## Discussion

Discuss your results here.

***

## Appendix

Place potential additional information here.
